Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}

### 2020-07-07 NetworkSlicing/report3.tex
ns

Game theory is generally defined as the mathematics of conflicts and are being utilized in various fields like economy, psychology, AI, sociology etc. In Game theory w.r.t RL, the policy is the strategy, mapping all possible state of actions, in respect to one of the players of the game.
The types of games in Multi-Agent RL (MARL) are:
● Static Games : players are independent and make simultaneous decision
● Stage Games : the rules depend on specific stages
● Repeated Games : when a game is played in sequence
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{rlfig}
  \caption{Multiple agents acting in the same environment \cite{rl1}}
  \label{fig:qos}
\end{figure}
%%
An extension of the single agent Markov decision process (MDP) to the multi-agent
case can be defined by Markov Games. In a Markov Game, joint actions are the
result of multiple agents choosing an action independently.
While in normal form games the challenges for reinforcement learners originate
mainly from the interactions between the agents, in Markov games they face the
additional challenge of an environment with state transitions. This means that the
agents typically need to combine coordination methods or equilibrium solvers used
in repeated games with MDP approaches from single-agent RL.
\item  \textbf{Find best delay formula which is the nearest to reality (M/M/1 M/D/1 M/G/1)}

\end{enumerate}

>>>>

Game theory is generally defined as the mathematics of conflicts and are being utilized in various fields like economy, psychology, AI, sociology etc. In Game theory w.r.t RL, the policy is the strategy, mapping all possible state of actions, in respect to one of the players of the game.
The types of games in Multi-Agent RL (MARL) are:
● Static Games : players are independent and make simultaneous decision
● Stage Games : the rules depend on specific stages
● Repeated Games : when a game is played in sequence
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{rlfig}
  \caption{Multiple agents acting in the same environment \cite{rl1}}
  \label{fig:qos}
\end{figure}
%%
An extension of the single agent Markov decision process (MDP) to the multi-agent
case can be defined by Markov Games. In a Markov Game, joint actions are the
result of multiple agents choosing an action independently.
While in normal form games the challenges for reinforcement learners originate
mainly from the interactions between the agents, in Markov games they face the
additional challenge of an environment with state transitions. This means that the
agents typically need to combine coordination methods or equilibrium solvers used
in repeated games with MDP approaches from single-agent RL.
\item  \textbf{Find best delay formula which is the nearest to reality (M/M/1 M/D/1 M/G/1)}
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{delay1}
  \caption{ Latency contribution in E2E delay of a packet transmission \cite{delay}}
  \label{fig:delay}
\end{figure}
In the LTE system, the latency can be divided into two
major parts: (1) user plane (U-plane) latency and (2) control
plane (C-plane) latency. The U-plane latency is measured by 
one directional transmit time of a packet to become available
in the IP layer between evolved UMTS terrestrial radio access
network (E-UTRAN) edge/UE and UE/E-UTRAN node.
On the other hand, C-plane latency can be defined as the
transition time of a UE to switch from idle state to active
state. At the idle state, an UE is not connected with radio
resource control (RRC). After the RRC connection is being
setup, the UE switches from idle state into connected state
and then enters into active state after moving into dedicated
mode. Since the application performance is dependent mainly
on the U-plane latency, U-plane is the main focus of interest
for low latency communication.
In the U-plane, the delay of a packet transmission in a
cellular network can be contributed by the RAN, backhaul,
core network, and data center/Internet.
\begin{equation}
T = T_{Radio} + T_{Backhaul} + T_{Core} + T_{Transport}
\end{equation}
\begin{itemize}
\item TRadio

 is the packet transmission time between eNB and
UEs and is mainly due to physical layer communication.
It is contributed by eNBs, UEs and environment. It
consists of time to transmit, processing time at eNB/UE,
retransmissions, and propagation delay. Processing delay at the eNB involves channel coding, rate matching,
scrambling, cyclic redundancy check (CRC) attachment,
precoding, modulation mapper, layer mapper, resource
element mapper, and OFDM signal generation. On the
other hand, uplink processing at UE involves CRC attachment, code block segmentation, code block concatenation, channel coding, rate matching, data and control
multiplexing, and channel interleaver. Propagation delay
depends on obstacles (i.e. building, trees, hills etc.) on
the way of propagation and the total distance traveled by
the RF signal;
\item TBackhaul

 is the time for building connections between
eNB and the core network (i.e. EPC). Generally, the core
network and eNB are connected by copper wires or microwave or optical fibers. In general, microwave involves
lower latency while optic fibers come with comparatively
higher latency. However, spectrum limitation may curb
the capacity of microwave ;
\item TCore

 is the processing time taken by the core network.
It is contributed by various core network entities such
as mobility management entity (MME), serving GPRS
support node (SGSN), and SDN/NFV. The processing
steps of core network includes NAS security, EPS bearer
control, idle state mobility handling, mobility anchoring,
UE IP address allocation, and packet filtering;
\item TTransport

 is the delay to data communication between
the core network and Internet/cloud. Generally, distance
between the core network and the server, bandwidth, and
communication protocol affect this latency
\end{itemize}
\begin{equation}
T_{Radio} = t_{Q} + t_{FA} + t_{tx} + t_{bsp} + t_{mpt}
\end{equation}
\begin{itemize}
\item tQ is the queuing delay which depends on the number of
users that will be multiplexed on same resources;
\item tFA is the delay due to frame alignment which depends on
the frame structure and duplexing modes (i.e., frequency
division duplexing (FDD) and time division duplexing
(TDD));
\item ttx is the time for transmission processing, and payload
transmission which uses at least one TTI depending on
radio channel condition, payload size, available resources,
transmission errors and retransmission;
\item tbsp is the processing delay at the base station;
\item  tmpt is the processing delay of user terminal. Both
the base station and user terminal delay depend on the
capabilities of base station and user terminal (i.e., UE),
respectively.
\end{itemize}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda$.
It is assumed that there are load balancers in each layer for each slice to divide the incoming traffic to VNFs equally \cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as an M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay of  slice, modeled as M/M/1 queue, is formulated as follow, respectively
\begin{equation}
d = \frac{1}{\mu - \alpha/{M}}
\end{equation}
where $1/\mu$ is the mean service time.
Besides, $\alpha$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The  arrival rate of each VNF in each layer of the slice $s$ is $\alpha/{M}$.
In addition, $d_{tr}$ is the transmission delay on the  wireless link. The arrival data rate of wireless link
 is equal to the arrival data rate of load balancers for each slice \cite{frdl}.
Moreover, it is assumed that the service time of transmission queue has
 an exponential distribution with mean $1/(R_{{tot}})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,
the mean delay of the transmission layer is
\begin{equation}
 d_{tr} = \frac{1}{R_{{tot}} - \alpha};
\end{equation}
where, $R_{{tot}}$ is the total achievable rate of each slice that is mapped to specific service.
Mean delay of each slice is obtained as below.
\begin{equation}
D_{s} = d+ d_{{tr}}
\end{equation}
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{delay}
  \caption{ delay of a packet \cite{frdl}}
  \label{fig:delay}
\end{figure}
\item \textbf{Assume a system model for the paper}

Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $ consists of $U_v$
 UEs that require certain service. Each slice $s \in \{1,2,...,S \}$  contains VNFs.
There are processing layer in the  system,  represented with a VNF.

Assume we have $M$ VNFs for processing data.
Each VNF  belongs to one or more slices. So, in the $s^{th}$ slice, there are $M_{s}$ VNFs. The VNFs have the computational capacity that is  equal to $\mu$.

Each VNF requires
physical resources that contain memory, storage and CPU.
Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
\begin{equation}
\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \},
\end{equation}
where $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
Moreover, the total amount of required memory, storage and CPU of all VNFs of a slice is defined as
\begin{equation}
\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.
\end{equation}
Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
\begin{equation*}
\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \},
\end{equation*}
In this system model, the assignment of physical DC resources to VNFs is considered. Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is connected to the VNFs of $s^{th}$ slice or not.
Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
$\phi_{s,d}$. So the total power of the system for all active DCs that are connected to slices can be represented as
\begin{equation*}
\textstyle \phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.
\end{equation*}
Also, a cost function for the placement of VNFs into DCs is defined as
\begin{equation}\label{eqpsi}
\textstyle  \psi_{tot} = \phi_{tot} - \nu \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s}
\end{equation}
where, $\nu$ is a design variable to value between the first term of \eqref{eqpsi} which is the total power consumption of physical resources and the second term that is shown the amount of admitted slices to have physical resources.
\begin{subequations}
\begin{alignat}{4}
\min\limits_{\boldsymbol{y} }   \quad &   \psi_{tot}(\boldsymbol{Y})\\
\text{s. t.} \quad & \textstyle \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} \forall s, \\
 &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}
\end{alignat}
\end{subequations}
\end{enumerate}
